---
title: "Analysis Report"
author: "Thoriq Aufar Nubli"
date: "2024-05-19"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This report provides a detailed analysis of retail data to uncover trends, patterns, and insights that can inform business decisions.

```{r library, include=FALSE}
library(tidyverse)
library(janitor)
library(readxl)
```

```{r data loading, include=FALSE}
sales_data = read_excel("C:/Users/thori/Desktop/Bismillah Kerja/Portofolio/RStudio/Portofolio_Data Analyst_1/walmart Retail Data.xlsx")
```

# Data Overview
```{r data overview, echo=FALSE}
sales_data = sales_data %>% 
  clean_names()

glimpse(sales_data)
```

```{r data transform, include=FALSE}
sum(is.na(sales_data))

sales_data = sales_data %>% 
  drop_na()

sales_data = sales_data %>% 
  mutate(month = month(order_date, label = TRUE),
         year = year(order_date))
```

```{r data processing, include=FALSE}
monthly_sales = sales_data %>% 
  group_by(year, month) %>% 
  summarise(total_sales = sum(order_quantity))

peak_sales_period = monthly_sales %>% 
  arrange(desc(total_sales)) %>% 
  head(1)

category_sales = sales_data %>% 
  group_by(product_sub_category) %>% 
  summarise(total_sales = sum(order_quantity)) %>% 
  arrange(desc(total_sales))

top_profit_sales_by_category = sales_data %>% 
  group_by(product_sub_category) %>% 
  summarise(total_profit = sum(profit)) %>% 
  arrange(desc(total_profit))

top_10_sales_by_state = sales_data %>% 
  group_by(state) %>% 
  summarise(total_sales = sum(order_quantity)) %>% 
  arrange(desc(total_sales)) %>% 
  head(10)
```

# Exploratory Data Analysis (EDA)
### Sales Over Time
```{r data viz monthly sales, echo=FALSE}
ggplot(monthly_sales, aes(x = month, y = total_sales, group = year, color = factor(year))) +
  geom_line() +
  labs(title = "Monthly Sales Over Years", x = "Month", y = "Sales") +
  theme_minimal() +
  theme(legend.title = element_blank())
```

### Sales by Category
```{r data viz sales by category, echo=FALSE}
ggplot(category_sales, aes(x = reorder(product_sub_category, total_sales), y = total_sales, fill = product_sub_category)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Sales by Category", x = "Category", y = "Total Sales") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  geom_text(aes(label = total_sales), vjust = 0.3, hjust = 1.2)
```

### Total Profit by Category
```{r data viz total profit by category, echo=FALSE}
ggplot(top_profit_sales_by_category, aes(x = reorder(product_sub_category, total_profit), y = total_profit, fill = product_sub_category)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Category", y = "Total Sales") +
  theme_minimal() +
  theme(legend.title = element_blank())
```

### Top 10 States with the Most Order
```{r data viz top 10 states, echo=FALSE}
ggplot(top_10_sales_by_state, aes(x = reorder(state, total_sales), y = total_sales, fill = state)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Top 10 Sales by State", x = "State", y = "Total Sales") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  geom_text(aes(label = total_sales), vjust = 0.3, hjust = 1.2)
```

# Key Insights
### Summary of Findings
* **Sales Trends:** Monthly sales show a fluctuating trend, with the highest peak in May each year.
* **Top Categories:** Categories such as “Paper”, “Phones and Communications”, and “Binders and Binders Accessories” contributed the most to overall sales.
* **Top Profit:** Categories such as “Telephone and Communications” and “Fastening and Fastening Accessories” are the top 2 categories with the highest profits. Even though "Paper" is the category with the highest sales, it does not make "Paper" the category with the highest profits.
* **Loss Category:** There are 3 categories that are losing money, namely "Scissors, Rulers and Trimmers", "Bookshelves", and "Tables".
* **Most Orders State:** California is the state with the most orders.

### Recomendations
* **Focus on High-Profit Categories:** Increase marketing and inventory for top-profit categories to maximize sales.
* **Product Strategy:** Consider promoting your best-selling products more aggressively.
* **Investigate some things further:** Conduct further investigation to find out the causes of fluctuating sales and loss-making categories.

### Conclussion
This retail analysis report provides valuable insights into sales trends and product performance. By leveraging these insights, the company can make informed decisions to drive growth and profitability.





